Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Duplicated word

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}

@@

\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
of subgraph isomorphism algorithms was the single strongest solver portfolios \citep{thelionpaper}.
As well as the modifications to solve $k$-less and induced problems, we have made two
simplifications: we do not use conflict-directed backjumping, and we do not use iterated label
filtering to recalculate neighbourhood degree sequences if vertices are not present in any target
domain after construction---in preliminary experiments, these techniques were not beneficial for $k
> 0$. We also do not strip isolated vertices, as this is not a valid simplification in the induced
case.

>>>>

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[vlined]{algorithm2e}

@@

\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
As well as the modifications to solve $k$-less and induced problems, we have made two
simplifications: we do not use conflict-directed backjumping, and we do not use iterated label
filtering to recalculate neighbourhood degree sequences if vertices are not present in any target
domain after construction---in preliminary experiments, these techniques were not beneficial for $k
> 0$. We also do not strip isolated vertices, as this is not a valid simplification in the induced
case.
